---
title: "Compare Performance"
date: "3/12/2020"
params: 
  authors: "Poornima Belavadi, Nils Plettenberg, Johannes Nakayama, André Calero Valdez"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(microbenchmark)
library(tidyverse)
library(glue)
library(here)
library(magrittr)
library(stats)
library(beepr)
if (FALSE) {
  if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
  
  BiocManager::install("HilbertCurve")
}

library(microbenchmark)
library(HilbertCurve)
library(gghilbertstrings)

source(here("R", "our_theme.R"))
theme_set(theme_bw() + my_theme)
```

#### `r params$authors` {-}

# Benchmarking gghilbertstrings

## Setup of the comparison

First, we decide how many repetitions we want for testing and how deep we want to go.

```{r benchmark_prep}
reps <- 10 #takes about 50 seconds on iMac i9 3.5GHz
size_exponent <- 11
```




## Running the benchmark
We run the creation of a coordinate system `r reps` times. This means creating 1 entry for every possible corner in the Hilbert Curve.


```{r benchmark, echo=TRUE, results='hide', class.source = 'fold-show'}
# Compare the creation of coordinate systems

mb <- list()
# The fast ones
for (i in 1:7) {
  df <- tibble(val = 1:4^i,
               size = runif(4^i, 1, 5),
               # create random sizes
               color = rep(c(1, 2, 3, 4), 4^(i - 1)))
  values <- df$val
  mb[[i]] <- microbenchmark(times = reps,
                     HilbertCurve = {
                       hc <- HilbertCurve(1, 4^i, level = i, newpage = FALSE)
                     },
                     gghilbertstrings = {
                       ggh <- hilbertd2xy(n = 4^i, values)
                     })
  
#print(i)
}
```


```{r benchmark2, echo=TRUE, results='hide', class.source = 'fold-show', cache=TRUE}
# These take a while
for (i in 8:12) {
  df <- tibble(val = 1:4^i,
               size = runif(4^i, 1, 5),
               # create random sizes
               color = rep(c(1, 2, 3, 4), 4^(i - 1)))
  values <- df$val
  mb[[i]] <- microbenchmark(times = reps,
                     HilbertCurve = {
                       hc <- HilbertCurve(1, 4^i, level = i, newpage = FALSE)
                     },
                     gghilbertstrings = {
                       ggh <- hilbertd2xy(n = 4^i, values)
                     })
  
#print(i)
}
```


```{r benchmark3, echo=TRUE, results='hide', class.source = 'fold-show'}
# Only our pkg has reasonable time. Large is not possible due to int64 limit.
for (i in 12:14) {
  df <- tibble(val = 1:4^i,
               size = runif(4^i, 1, 5),
               # create random sizes
               color = rep(c(1, 2, 3, 4), 4^(i - 1)))
  values <- df$val
  mb[[i]] <- microbenchmark(times = reps,
                     gghilbertstrings = {
                       ggh <- hilbertd2xy(n = 4^i, values)
                     })
  
}

res <- data.frame()

for (i in 1:length(mb)) {
  tmp <- mb[[i]] %>% as_tibble() %>% mutate(depth = i)  
  res <- res %>% bind_rows(tmp)
}

library(ggdark)
library(scales)
res %>% mutate(time = time/1000) %>% 
  ggplot() + 
  aes(x = depth, y = time, color = expr) + 
  geom_jitter(width = 0.1, height = 0, alpha = 0.2) +
  geom_smooth() + 
  scale_y_log10(labels = comma) +
  scale_x_continuous(breaks = 3:14, minor_breaks = NULL) +
  scale_color_viridis_d(begin = 0.5, end = 0.8, option = "D") +
  labs(x = "Order of Hilbert Curve", y = "Time in ms (log-scale)", color = "Package",
       title = "Our package is two orders of magnitute faster",
       subtitle = glue("Comparison of {reps} repetitions across all orders."),
       caption = "Order 14 means 268,435,456 coordinates") +
  theme_dark() +
  theme(
  plot.background = element_rect(fill = "grey50", color = "grey50"),
  plot.title = element_text(color = "white"),
  plot.subtitle = element_text(color = "white"),
  plot.margin = margin(15, 15, 15, 15),
  plot.caption = element_text(color = "white"),
  panel.background = element_rect(fill = "grey30", color = "grey50"),
  panel.grid = element_line(color = "grey50", size = 1),
  axis.title.x = element_text(color = "white"),
  axis.title.y = element_text(color = "white"),
  axis.text = element_text(color = "white"),
  legend.background = element_rect(fill = "gray30"),
  legend.text = element_text(color = "white"),
  legend.title = element_text(color = "white")
)
  
ggsave("output/performance.pdf")

```



# Plotting the results

The following restuls highlight these findings for $4^8$ entries.

```{r}
# extract benchmark data
expression <- mb[[8]]$expr
time <- mb[[8]]$time

measured_times <- data.frame(
  expression = expression,
  times = time
)

measured_times %<>% mutate(times = times / 1000000)

measured_times %>%
  group_by(expression) %>%
  filter(
    times < stats::quantile(.$times, 0.95) 
    & times > stats::quantile(.$times, 0.05)
  ) -> measured_times_cropped

# plot
measured_times_cropped %>% 
  ggplot(aes(x = expression, y = times)) +
  geom_violin(color = "transparent", fill = "gold2", alpha = 0.5) +
  coord_flip() +
  labs(
    title = glue("Comparison on {reps} runs [0.05 - 0.95 percentile]"),
    y = "Time [milliseconds]",
    caption = "Red dashed lines indicate median execution times."
  ) +
  geom_hline(
    yintercept = median(
      (measured_times_cropped %>% filter(expression == "gghilbertstrings"))$times
    ),
    linetype = "dashed",
    color = "firebrick",
    size = 1
  ) +
  geom_hline(
    yintercept = median(
      (measured_times_cropped %>% filter(expression == "HilbertCurve"))$times
    ),
    linetype = "dashed",
    color = "firebrick",
    size = 1
  ) +
  theme(
    plot.background = element_rect(fill = "grey50", color = "grey50"),
    plot.title = element_text(color = "white"),
    plot.margin = margin(15, 15, 15, 15),
    panel.background = element_rect(fill = "grey30", color = "grey50"),
    panel.grid = element_line(color = "grey50", size = 1),
    axis.title.x = element_text(color = "white", margin = margin(t = 10, b = 10)),
    axis.title.y = element_blank(),
    axis.text = element_text(color = "white"),
    axis.ticks = element_blank(),
    legend.position = "None",
    plot.caption = element_text(color = "white")
  )

# save
ggsave(here::here("output", "benchmark.pdf"), width = 6.5, height = 3.5, dpi = 900)
```


# What is being tested here?

## gghilbertstrings

```{r show_plot, echo=TRUE, results='hide', class.source = 'fold-show'}
df <- tibble(val = 1:4^4,
               size = runif(4^4, 1, 5),
               # create random sizes
               color = rep(c(1, 2, 3, 4), 4^(4 - 1)))
gghilbertplot(df,
              val,
              color = factor(color),
              size = size,
              alpha = 0.5,
              add_curve = TRUE) +
  coord_fixed()
```

## HilbertCurve

```{r show_plot2, echo=TRUE, results='hide', class.source = 'fold-show'}
{
  hc <- HilbertCurve(s = 1, e = 256, level = 4, reference = TRUE)
  hc_points(hc, x1 = df$val, 
          gp = gpar(fill = c("white", "red", "blue", "green")))
}
```





```{r benchmark_plot, message=FALSE, warning=FALSE, eval=FALSE}
autoplot(mb) +
  coord_flip() +
  ggtitle(
    glue("Comparison of runtime performance using {reps} repetions on 4 levels")
    ) +
  labs(caption = "X-Axis on log-scale") +
  theme_bw()
```

## Results as a table
Values are miliseconds.

```{r benchmark_2}
mb[[8]] %>% 
  summary() %>% 
  as_tibble() 
```

```{r include=FALSE}
beep()
```
