---
title: "Demonstration DatenspendeBTW17"
date: "3/12/2020"
params:
  authors: "Anonymized"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# dependencies
library(tidyverse)
library(magrittr)
library(lubridate)
library(gghilbertstrings)
library(gganimate)
library(progress)
library(glue)
library(beepr)
library(ggnewscale)
library(patchwork)
library(gifski)
library(here)
source(here::here("R", "our_theme.R"))

# parameters
top_count <- 30

# is ffmpeg available?
ffmpeg <- FALSE
```

#### `r params$authors` {-}


# Reduced Hilbert Curve Demonstration

SOME DESCRIPTION HERE

```{r reduced_curve}
df <- data.frame(id = 1:129)
gghilbertstrings::gghilbertplot(df, id, add_curve = TRUE, alpha = 0, curve_color = "white") +
  geom_path(color = "seagreen1", size = 1) +
  coord_fixed() +
  labs(title = "Reduced curve") +
  theme(
    plot.background = element_rect(fill = "grey50", color = "transparent"),
    panel.background = element_rect(fill = "grey50", color = "transparent"),
    panel.grid = element_blank(),
    plot.title = element_text(size = 20, color = "white"),
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank()
  ) -> hilbert_overlay

ggarrange(hilbert_overlay) +
  theme(plot.background = element_rect(fill = "grey50", color = "transparent"))

ggsave(here::here("output", "reduced_curve.pdf"), width = 5, height = 5.5)
```


# Map Demonstration


## Read in the data

```{r read_data}
terms <- c("CDU", "AfD")
all_data <- NULL
for (chosen_term in terms) {
  all_data <- bind_rows(all_data, read_rds(here::here("data", glue("datenspende{chosen_term}.rds"))))
}

all_data <- all_data %>%
  mutate(search_date = as_date(search_date)) %>% # Fix date as only days
  mutate(domain = str_replace_all(domain, "^[.](.+)", "\\1")) %>%  # fix some broken domains
  mutate(url = str_replace_all(url, "^[.](.+)", "\\1"))

# how many days?
date_duration <- (all_data %>% pull(search_date) %>% unique() %>% max()) - 
  (all_data %>% pull(search_date) %>% unique() %>% min())

```

A total of `r nrow(all_data)` entries were in the data base. 
The earliest date is: `r all_data %>% pull(search_date) %>% unique() %>% min()` and the latest date is: `r all_data %>% pull(search_date) %>% unique() %>% min()`.
Total duration is `r date_duration`.


```{r create_coordinates}
# create coordinates for all possible urls and collect timing
{
  start.time <- Sys.time()
  all_data <- all_data %>%
    create_id_column(url)
  end.time <- Sys.time()
  time.taken <- end.time - start.time
  print(time.taken)
}

upper_limit <- max(all_data$gghid)
```

There were a total of `r upper_limit` coordinates created for the data set.


## Top domains

Which domains appeared most frequently in all our search results? We use these to create label anchors in the data set.


### Top Domain Visualization

```{r create_regions}
all_data %>% mutate(domain_number = as.numeric(factor(domain))) %>% pull(domain_number) %>% max()

# encode regions
regions <- all_data %>% 
  select(gghid, domain, url) %>% unique() %>% 
  mutate(domain_number = as.numeric(factor(domain))) %>%  ## used to be %% 2
  # mutate(domain_number = as.numeric(factor(domain)) %% 2) %>%  ## used to be %% 2
  mutate(domain_number = factor(domain_number)) %>% 
  create_coordinates(gghid) %>% 
  arrange(gghid)
```


```{r find_top_domains}
plot_terms <- all_data %>% 
  pull(keyword) %>% 
  unique() %>% 
  paste(collapse = ", ")

# find all domains that occur most frequently
top_domains <- all_data %>%
  group_by(domain) %>%
  count() %>%
  arrange(desc(n)) %>%
  head(top_count)

# take all urls to top domains
mean_positions <- all_data %>%
  select(domain, gghid) %>%
  right_join(top_domains) %>%
  bind_rows(tibble(domain = c("aaaa","zzzz"), gghid = c(1,upper_limit))) %>% 
  create_coordinates(gghid) %>% 
  group_by(domain) %>%  # find the average domain position
  summarize(x = round(mean(x),2),  
            y = round(mean(y),2)
            ) %>% 
  ungroup()

# add artificial start and endpoints to the label data to prevent truncated coordinate system
label_positions <- mean_positions %>%
 # bind_rows(tibble(domain = c("aaaa","zzzz"), gghid = c(1,upper_limit))) %>%
 # create_coordinates(gghid) %>%
  filter(!str_detect(domain, "aaaa")) %>%
  filter(!str_detect(domain, "zzzz"))
```


## Background Map

```{r location_small}
# generics 
set.seed(3)
n_colors <- dim(regions %>% select(domain_number) %>% unique())[1]
color_scheme <- grDevices::topo.colors(n_colors) %>% sample()

# preview label positions
label_positions %>%
  ggplot() +
  aes(x = x) +
  aes(y = y) +
  aes(label = domain) +
  scale_color_manual(values = color_scheme) +
  scale_fill_manual(values = color_scheme) +
  geom_point(
    data = regions,
    mapping = aes(x = x, y = y, color = domain_number, group = "1"),
    alpha = 0.3,
    size = 1.2,
    shape = 15
  ) +
  guides(color = FALSE) +
  theme(
    legend.position = "none",
    axis.title = element_blank(),
    axis.text = element_blank()
  ) +
  ggrepel::geom_label_repel(
    seed = 123, 
    size = 2, 
    show.legend = F, 
    min.segment.length = 0, 
    color = "white",
    fill = "black"
  ) +
  coord_fixed() +
  scale_x_continuous(expand = c(0, 0), limits = c(0, NA)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  labs(
    title = paste("Locations of top", top_count, "search results"),
    subtitle = paste("Websites for terms:", plot_terms),
    caption = paste("Mean location and regions of ", upper_limit, "URLs")
  ) +
  my_theme +
  theme(
    plot.margin = margin(5, 5, 5, 5),
    panel.grid = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) +
  NULL -> locations_small

ggpubr::ggarrange(locations_small) +
  theme(
    plot.background = element_rect(fill = "grey50", color = "grey50"),
    plot.title = element_text(color = "white"),
    plot.subtitle = element_text(color = "white"),
    plot.margin = margin(2, 2, 2, 2),
    plot.caption = element_text(color = "white"),
    panel.background = element_rect(fill = "grey50", color = "grey50"),
    panel.grid = element_line(color = "grey50", size = 1),
    axis.title.x = element_text(color = "white"),
    axis.title.y = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    legend.position = "None"
  )

# ggsave(filename = here("output", "locationssmall.pdf"), width = 6, height = 5)
ggsave(filename = here("output", "locationssmall.png"), width = 5, height = 5.5)
```


## Comparison over Time

```{r comparison_over_time}
# generics 
n_colors <- dim(regions %>% select(domain_number) %>% unique())[1]
color_scheme <- grDevices::topo.colors(n_colors) %>% sample()

# format data
all_data %>% 
  filter(country == "DE") %>% 
  filter(
    #search_date == "2017-09-22" |
    search_date == "2017-09-23" |
    search_date == "2017-09-24"
  ) %>% 
  mutate(rank = 10 - rank) %>% 
  filter(rank > 0) %>% 
  mutate(rank = factor(rank, levels = c(1:10), labels = paste("Rank", 10:1))) %>% 
  create_coordinates(gghid) -> plot_data

# plot
ggplot(plot_data) +
  scale_color_manual(values = color_scheme) +
  geom_point(
    data = regions,
    mapping = aes(x = x, y = y, color = domain_number, group = "1"),
    alpha = 0.1,
    size = 2,
    shape = 15
  ) +
  new_scale_color() +
  geom_point(
    data = plot_data,
    mapping = aes(x = x, y = y, color = keyword, size = as.numeric(rank)),
    color = "white",
    alpha = 0.1,
    shape = 16
  ) +
  ggrepel::geom_label_repel(
    data = label_positions,
    mapping = aes(x = x, y = y, label = domain),
    seed = 123,
    size = 2,
    show.legend = F,
    min.segment.length = 0,
    segment.size = 0.3,
    fill = "black",
    color = "grey80",
    alpha = 0.7
  ) +
  coord_fixed() +
  facet_grid(rows = vars(search_date), cols = vars(keyword)) +
  my_theme +
  theme(
    panel.grid = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) -> singleplot

ggarrange(singleplot)  +
  theme(
    plot.background = element_rect(fill = "grey50", color = "grey50"),
    plot.margin = margin(2, 2, 2, 2),
    panel.background = element_rect(fill = "grey50", color = "grey50"),
    panel.grid = element_line(color = "grey50", size = 1),
    legend.position = "None"
  )

# save
ggsave(here::here("output", "multiframe.png"), width = 8, height = 10)
```



```{r beep, include=FALSE}
beep()
```
