---
title: "Datenspende Analysis with gghilberstrings"
author: "André Calero Valdez"
date: "7/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(gghilbertstrings)
library(gganimate)
library(progress)
library(glue)
library(beepr)


# Parameters

# where is the data?
pth <- here::here()
# should I recreate the data from original raw CSV data?
create_rds_files_from_csv <- FALSE
top_count <- 30
```


# Some helper functions for data

```{r functions}
# get all entry names for file system
get_terms <- function(){
  #files <- dir(pth, pattern = ".*csv")
  #terms <- str_match(files,"(.*)_.{2}.csv")[,2] %>% unique()
  #terms
  c("AfD", "CDU")
}


# function to write a term file in XZ compressed format
write_terms_rds <- function(term){
  stop("This function only works when the raw data is available, which is not shared in this repository.")
  options(readr.show_progress = FALSE)
  #read files
  files <- dir(pth, pattern = paste0(".*",term,".*.csv"), full.names = T)
  all_data <- NULL
  # setup progress bar
  pb <- progress_bar$new(
    format = paste("Reading", term, "[:bar] :percent eta: :eta"),
    total = length(files), clear = FALSE, width= 100)

  # read files
  for (file in files) {
    suppressMessages(
      suppressWarnings(
        file_data <- read_csv(file) %>% dplyr::rename(uuid = X1)
      )
    )

        all_data <- bind_rows(all_data, file_data)
    pb$tick()
  }

  message("Term: ", term, " has ", nrow(all_data), " entries. Compressing file ...")
  write_rds(all_data, here::here("debugging", paste0("datenspende",term, ".rds")), compress = "xz")
  message("Done.")
  options(readr.show_progress = TRUE)
}
```







# Keywords in the data set and colors

```{r write_data}
terms <- get_terms()

if(create_rds_files_from_csv){
  # run only on subset?
  term_selection <- terms #head(terms)
  i <- 1

  total <- length(term_selection)
  for (term in term_selection) {
    print(glue("Running {i} of {total} {Sys.time()}"))
    write_terms_rds(term)
    i <- i + 1
  }
}
terms

party_colors <- c("#009EE0", # AFD blue
                  "#111111") # CDU black (as gray)
                  #"#009EE0", "#000000", "#46962B", "#000000", 
                  #"#46962B", "#ff00ff", "#000000", "#4b0082", "#4b0082", "#FF00FF",
                  #"#46962B", "#FF0000", "#4b0082", "#FF0000")
```



# Read in the data

```{r read_data}
####
#### ----------------- READ LOOP STARTS here
####

selector <- c(1,2)

selected_terms <- terms[selector]
selected_colors <- party_colors[selector]
all_data <- NULL
for (chosen_term in selected_terms) {
  all_data <- bind_rows(all_data,
                        read_rds(here::here(glue("datenspende{chosen_term}.rds")))
                        )
}
cat("Files (14 MB) were read.")
beep()

all_data <- all_data %>%
  mutate(search_date = as_date(search_date)) %>% # Fix date as only days
  mutate(domain = str_replace_all(domain, "^[.](.+)", "\\1")) %>%  # fix some broken domains
  mutate(url = str_replace_all(url, "^[.](.+)", "\\1"))



date_duration <- all_data %>% pull(search_date) %>% unique() %>% max() - all_data %>% pull(search_date) %>% unique() %>% min()

```

A total of `r nrow(all_data)` entries were in the data base. 
The earliest date is: `r all_data %>% pull(search_date) %>% unique() %>% min()` and the latest date is: `r all_data %>% pull(search_date) %>% unique() %>% min()`.
Total duration is `r date_duration`.

```{r create_coordinates}
# create coordinates for all possible urls and collect timing
{
  start.time <- Sys.time()
  all_data <- all_data %>%
    create_id_column(url)
  end.time <- Sys.time()
  time.taken <- end.time - start.time
  print(time.taken)
  beep()
}

upper_limit <- max(all_data$gghid)
```

There were a total of `r upper_limit` coordinates created for the data set.


# Theme Setup
```{r theme_setup}

my_theme <- theme_void() +
   theme(
    panel.background = element_rect(fill = "#EEEEEE", color = "#EEEEEE")
    #plot.margin = margin(t = 3, r = 10, b = 3, l = 10, unit = "pt")
    #panel.grid = element_line(color = "#DDDDDD") 
  )
  

```

## Top domains
Which domains appeared most frequently in all our search results? We use these to create label anchors in the data set.


### Top Domain Visualization

```{r test color path}


all_data %>% mutate(domain_number = as.numeric(factor(domain))) %>% pull(domain_number) %>% max()

# create an alternating path variable for color coding
all_data %>% 
  select(gghid, domain, url) %>% unique() %>% 
  mutate(domain_number = as.numeric(factor(domain)) %% 2) %>% 
  mutate(domain_number = factor(domain_number)) %>% 
  create_coordinates(gghid) %>% 
  arrange(gghid) -> regions
  


```


```{r find_top_domains}
plot_terms <- all_data %>% pull(keyword) %>% unique() %>% paste(collapse = ", ")
# find all domains that occur most frequently
top_domains <- all_data %>%
  group_by(domain) %>%
  count() %>%
  arrange(desc(n)) %>%
  head(top_count)

# take all urls to top domains
mean_positions <- all_data %>%
  select(domain, gghid) %>%
  right_join(top_domains) %>%
  bind_rows(tibble(domain = c("aaaa","zzzz"), gghid = c(1,upper_limit))) %>%
  create_coordinates(gghid) %>% 
  group_by(domain) %>%  # find the average domain position
  summarize(x = round(mean(x),2),  
            y = round(mean(y),2)
            ) %>% 
  ungroup()

# add artificial start and endpoints to the label data to prevent truncated coordinate system
label_positions <- mean_positions %>%
 # bind_rows(tibble(domain = c("aaaa","zzzz"), gghid = c(1,upper_limit))) %>%
 # create_coordinates(gghid) %>%
  filter(!str_detect(domain, "aaaa")) %>%
  filter(!str_detect(domain, "zzzz"))


library(ggnewscale)

#preview label positions
label_positions %>%
  ggplot() +
  scale_color_manual(values = c("#0000FF", "#FFFF00")) +
  geom_path(data = regions, mapping = aes(x = x, y = y, color = domain_number, group = "1"), alpha = 0.4) +
#  new_scale_color() +
  guides(color = FALSE) +
  theme(legend.position="none") +
  aes(x = x) +
  aes(y = y) +
  aes(label = domain) +
  ggrepel::geom_label_repel(seed = 123, size = 2, show.legend = F, min.segment.length = 0, color = "black") +
  my_theme +
  coord_fixed() +
  scale_x_continuous(expand = c(0, 0), limits = c(0,NA)) + scale_y_continuous(expand = c(0, 0), limits = c(0,NA)) +
  labs(title = paste("Locations of top", top_count, "search results"),
       subtitle = paste("Websites for terms:", plot_terms),
       caption = paste("Mean location and regions of ",upper_limit, "URLs"))


ggsave(filename = "locationssmall.pdf", width = 4, height = 2.5)

```




# Single Frame Visualization

```{r single_frame}

repel_label <- ggrepel::geom_label_repel(data = label_positions,
                                         mapping = aes(x = x, y = y, label = domain),
                                         seed = 123, size = 2, show.legend = F, min.segment.length = 0, color = "black")

label_label <- geom_text(data = label_positions,
                                         mapping = aes(x = x, y = y, label = domain), color = "gray")


path_data <- data.frame(gghid = c(1:upper_limit)) %>% create_coordinates(gghid)

all_data %>%
  #filter(keyword %in% c("AfD", "CDU")) %>% 
  mutate(rank = 10 - rank) %>% 
  filter(rank > 1) %>%
  mutate(rank = factor(rank, levels = c(0:10), labels = paste("Rank", 11:1))) %>% 
  filter(search_type == "search") %>%
  filter(country == "DE") %>%
  filter(search_date == "2017-09-20") %>% pull(person_id) %>% n_distinct() 



all_data %>%
  #filter(keyword %in% c("AfD", "CDU")) %>% 
  mutate(rank = 10 - rank) %>% 
  filter(rank > 0) %>%
  mutate(rank = factor(rank, levels = c(0:10), labels = paste("Rank", 11:1))) %>% 
  filter(search_type == "search") %>%
  filter(country == "DE") %>%
  filter(search_date == "2017-09-20") %>%
  create_coordinates(gghid) %>%
  mutate(rank = as.factor(rank)) %>% 
  ggplot() +
  scale_color_manual(values = c("#0000FF", "#FFFF00"), guide = "none") +
  geom_path(data = regions, mapping = aes(x=x,y=y, color = domain_number, group = "1"), inherit.aes = FALSE, alpha = 0.3) +
  labs(color = "Region") +
  guides(color = FALSE) +
  new_scale_color() +
  scale_color_manual(values = selected_colors) +
  aes(x = x, y = y, color = keyword, label = domain)+ #, size = rank) +
  repel_label +
  #label_label+
  geom_point(aes(size = rank), alpha = 0.01) +
  labs(title = "Hilbert Plot for top search results for AfD and CDU", size = "Rank", color = "Search Term",
       subtitle = "Differences for the AfD and CDU, Date: 2017-09-20",
       caption = paste("Results for 1298 unique users. Individual results use 0.01 alpha blending.")) +
  #coord_fixed() +
  #facet_wrap(~keyword, nrow = 1) +
  guides(colour = guide_legend(override.aes = list(alpha = 1, size = 5))) +
  guides(size = guide_legend(override.aes = list(alpha = 0.5))) +
  my_theme -> singleplot
singleplot


ggsave(plot = singleplot, filename = "singleframe.pdf", width = 8, height = 5)
```




# Two Frames

```{r}
library(patchwork)

all_data %>%
  #filter(keyword %in% c("AfD", "CDU")) %>% 
  mutate(rank = 10 - rank) %>% 
  filter(rank > 0) %>%
  mutate(rank = factor(rank, levels = c(0:10), labels = paste("Rank", 11:1))) %>% 
  filter(search_type == "search") %>%
  filter(country == "DE") %>%
  filter(search_date == "2017-09-20") %>%
  create_coordinates(gghid) %>%
  mutate(rank = as.factor(rank)) %>% 
  ggplot() +
  scale_color_manual(values = c("#0000FF", "#FFFF00"), guide = "none") +
  geom_path(data = regions, mapping = aes(x=x,y=y, color = domain_number, group = "1"), inherit.aes = FALSE, alpha = 0.3) +
  labs(color = "Region") +
  guides(color = FALSE) +
  new_scale_color() +
  scale_color_manual(values = selected_colors) +
  aes(x = x, y = y, color = keyword, label = domain)+ #, size = rank) +
  repel_label +
  #label_label+
  geom_point(aes(size = rank), alpha = 0.01) +
  guides(colour = guide_legend(override.aes = list(alpha = 1, size = 5))) +
  guides(size = guide_legend(override.aes = list(alpha = 0.5))) +
  guides(size = FALSE) +
  guides(colour = FALSE) +
  labs(subtitle = "Date: 2017-09-20") +
  my_theme -> singleplot1


all_data %>%
  #filter(keyword %in% c("AfD", "CDU")) %>% 
  mutate(rank = 10 - rank) %>% 
  filter(rank > 0) %>%
  mutate(rank = factor(rank, levels = c(0:10), labels = paste("Rank", 11:1))) %>% 
  filter(search_type == "search") %>%
  filter(country == "DE") %>%
  filter(search_date == "2017-09-24") %>%
  create_coordinates(gghid) %>%
  mutate(rank = as.factor(rank)) %>% 
  ggplot() +
  scale_color_manual(values = c("#0000FF", "#FFFF00"), guide = "none") +
  geom_path(data = regions, mapping = aes(x=x,y=y, color = domain_number, group = "1"), inherit.aes = FALSE, alpha = 0.3) +
  labs(color = "Region") +
  guides(color = FALSE) +
  new_scale_color() +
  scale_color_manual(values = selected_colors) +
  aes(x = x, y = y, color = keyword, label = domain)+ #, size = rank) +
  repel_label +
  #label_label+
  geom_point(aes(size = rank), alpha = 0.01) +
  guides(colour = guide_legend(override.aes = list(alpha = 1, size = 5))) +
  guides(size = guide_legend(override.aes = list(alpha = 0.5))) +
  guides(size = FALSE) +
  guides(colour = FALSE) +
  labs(subtitle = "Date: 2017-09-24") +
  my_theme -> singleplot2

singleplot

fullplot <- singleplot1 + singleplot2 + plot_annotation(title = "Hilbert Plot for top search results for AfD and CDU",
                                                        caption = paste("Results for 1298 unique users. Individual results use 0.01 alpha blending."))


fullplot 

ggsave(plot = fullplot, filename = "sbs.pdf", width = 8, height = 5)
```



```{r}
beep(2)
```







# Animation

```{r generate_animation_data}
anim_data <- all_data %>%
  mutate(rank = 10 - rank) %>% 
  filter(rank > 0) %>%
  mutate(rank = factor(rank, levels = c(0:10), labels = paste("Rank", 11:1))) %>% 
  filter(search_type == "search") %>%
  filter(country == "DE") %>%
  filter(search_date > "2017-09-20") %>%  
  create_coordinates(gghid) %>%
  mutate(rank = as.factor(rank))  

anim_data %>% pull(search_date) %>% unique() %>% length() -> frame_pred
```


```{r generate_animation}
repel_label <- ggrepel::geom_label_repel(data = label_positions,
                                         mapping = aes(x = x, y = y, label = domain),
                                         seed = 123, size = 3, show.legend = F, min.segment.length = 0, color = "black")

anim_data %>%
  ggplot() +
  scale_color_manual(values = c("#0000FF", "#FFFF00"), guide = "none") +
  geom_path(data = regions, mapping = aes(x=x,y=y, color = domain_number, group = "1"), inherit.aes = FALSE, alpha = 0.3) +
  new_scale_color() + 
  aes(x = x, y = y, color = keyword, label = domain, size = rank) +
  scale_color_manual(values = selected_colors) +
  repel_label +
  #label_label+
  geom_point(alpha = 0.01) +
  labs(title = "Hilbert Plot for search results", size = "Rank", color = "Search Term",
       subtitle = "Date: {frame_time}") +
  coord_fixed() +
  #facet_wrap(~keyword) +
  guides(colour = guide_legend(override.aes = list(alpha = 1, size = 5))) +
  guides(size = guide_legend(override.aes = list(alpha = 0.5))) +
  my_theme +
  transition_time(search_date) +
  enter_appear() +
  exit_disappear() -> p

```

```{r render_preview}
# low res version
animate(p, renderer = gifski_renderer(), width = 1600, height = 1000, res = 150, fps = 1, duration = frame_pred)
anim_save("video.gif")
```


```{r create_mpg}


animate(p, renderer = ffmpeg_renderer(), width = 1920, height = 1080, fps = 1, duration = frame_pred, res = 200)
anim_save("output.mp4")
beep()
```


```{r render_full, eval=FALSE, include=FALSE}
# render animation
{
  animate(p, renderer = gifski_renderer(), width = 1200, height = 1200, res = 150, fps = 20, duration = 40)
  anim_save("test.gif")
  beep()
}
```






```{r end, include=FALSE}

all_data %>% select(domain, url) %>% head(50) %>% View()
beep(4)
```


