---
title: "Datenspende Analysis with gghilberstrings"
author: "Poornima Belavadi, Nils Plettenberg, Johannes Nakayama, André Calero Valdez"
date: "7/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(gghilbertstrings)
library(gganimate)
library(progress)
library(glue)
library(beepr)
library(ggnewscale)
library(patchwork)
library(gifski)
library(here)
# Parameters
top_count <- 30

# is ffmpeg available?
ffmpeg <- FALSE
```


# Keywords in the data set and colors

```{r create_colors}
terms <- c("CDU", "AfD")
party_colors <- c("#009EE0", # AFD blue
                  "#111111") # CDU black (as gray)
                  #"#009EE0", "#000000", "#46962B", "#000000", 
                  #"#46962B", "#ff00ff", "#000000", "#4b0082", "#4b0082", "#FF00FF",
                  #"#46962B", "#FF0000", "#4b0082", "#FF0000")
```



# Read in the data

```{r read_data}
####
#### ----------------- READ LOOP STARTS here
####

selector <- c(1,2)

selected_terms <- terms[selector]
selected_colors <- party_colors[selector]
all_data <- NULL
for (chosen_term in selected_terms) {
  all_data <- bind_rows(all_data,
                        read_rds(here::here("data", glue("datenspende{chosen_term}.rds")))
                        )
}

all_data <- all_data %>%
  mutate(search_date = as_date(search_date)) %>% # Fix date as only days
  mutate(domain = str_replace_all(domain, "^[.](.+)", "\\1")) %>%  # fix some broken domains
  mutate(url = str_replace_all(url, "^[.](.+)", "\\1"))


# how man days?
date_duration <-
  (all_data %>% 
     pull(search_date) %>% 
     unique() %>% 
     max())  - 
  (all_data %>% 
    pull(search_date) %>% 
    unique() %>%
    min() )

```

A total of `r nrow(all_data)` entries were in the data base. 
The earliest date is: `r all_data %>% pull(search_date) %>% unique() %>% min()` and the latest date is: `r all_data %>% pull(search_date) %>% unique() %>% min()`.
Total duration is `r date_duration`.

```{r create_coordinates}
# create coordinates for all possible urls and collect timing
{
  start.time <- Sys.time()
  all_data <- all_data %>%
    create_id_column(url)
  end.time <- Sys.time()
  time.taken <- end.time - start.time
  print(time.taken)
  beep()
}

upper_limit <- max(all_data$gghid)
```

There were a total of `r upper_limit` coordinates created for the data set.


# Theme Setup
```{r theme_setup}

my_theme <- theme_void() +
   theme(
    panel.background = element_rect(fill = "#EEEEEE", color = "#EEEEEE")
    #plot.margin = margin(t = 3, r = 10, b = 3, l = 10, unit = "pt")
    #panel.grid = element_line(color = "#DDDDDD") 
  )
  
my_theme2 <- theme(
    plot.background = element_rect(fill = "grey50", color = "grey50"),
    plot.title = element_text(color = "white"),
    plot.subtitle = element_text(color = "white"),
    plot.margin = margin(15, 15, 15, 15),
    plot.caption = element_text(color = "white"),
    panel.background = element_rect(fill = "grey30", color = "grey50"),
    panel.grid = element_line(color = "grey50", size = 1),
    axis.title.x = element_text(color = "white"),
    axis.title.y = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    legend.position = "None"
  )

```

## Top domains
Which domains appeared most frequently in all our search results? We use these to create label anchors in the data set.


### Top Domain Visualization

```{r test color path}
all_data %>% mutate(domain_number = as.numeric(factor(domain))) %>% pull(domain_number) %>% max()

# create an alternating path variable for color coding
regions <- all_data %>% 
  select(gghid, domain, url) %>% unique() %>% 
  mutate(domain_number = as.numeric(factor(domain))) %>%  ## used to be %% 2
  # mutate(domain_number = as.numeric(factor(domain)) %% 2) %>%  ## used to be %% 2
  mutate(domain_number = factor(domain_number)) %>% 
  create_coordinates(gghid) %>% 
  arrange(gghid)
```


# Describe something here.

```{r find_top_domains}
plot_terms <- all_data %>% 
  pull(keyword) %>% 
  unique() %>% 
  paste(collapse = ", ")

# find all domains that occur most frequently
top_domains <- all_data %>%
  group_by(domain) %>%
  count() %>%
  arrange(desc(n)) %>%
  head(top_count)

# take all urls to top domains
mean_positions <- all_data %>%
  select(domain, gghid) %>%
  right_join(top_domains) %>%
  bind_rows(tibble(domain = c("aaaa","zzzz"), gghid = c(1,upper_limit))) %>% 
  create_coordinates(gghid) %>% 
  group_by(domain) %>%  # find the average domain position
  summarize(x = round(mean(x),2),  
            y = round(mean(y),2)
            ) %>% 
  ungroup()

# add artificial start and endpoints to the label data to prevent truncated coordinate system
label_positions <- mean_positions %>%
 # bind_rows(tibble(domain = c("aaaa","zzzz"), gghid = c(1,upper_limit))) %>%
 # create_coordinates(gghid) %>%
  filter(!str_detect(domain, "aaaa")) %>%
  filter(!str_detect(domain, "zzzz"))
```


```{r location_small}
set.seed(3)

# happy little accidents
dimension_portal_1 <- geom_density_2d(
    data = regions,
    mapping = aes(x = x, y = y, color = domain_number, group = "1")
  )
dimension_portal_2 <- geom_density_2d_filled(
    data = regions,
    mapping = aes(x = x, y = y, color = domain_number, group = "1")
  )
polygon <- geom_polygon(
    data = regions,
    mapping = aes(x = x, y = y, fill = domain_number),
    color = "transparent"
  )
hex_bins <- geom_hex(
    data = regions,
    stat = "identity",
    mapping = aes(x = x, y = y, fill = domain_number)
  )

# plot generics 
n_colors <- dim(regions %>% select(domain_number) %>% unique())[1]
# color_scheme <- viridis::viridis(n_colors) %>% sample()
color_scheme <- grDevices::topo.colors(n_colors) %>% sample()
# color_scheme <- grDevices::terrain.colors(n_colors) %>% sample()
# color_scheme <- grDevices::rainbow(n_colors) %>% sample()
# color_scheme <- colorRamps::blue2red(n_colors) %>% sample()
# color_scheme <- colorRamps::ygobb(n_colors) %>% sample()
# color_scheme <- colorspace::rainbow_hcl(n_colors) %>% sample()
# color_scheme <- colorRamps::matlab.like(n_colors) %>% sample()



# preview label positions
label_positions %>%
  ggplot() +
  aes(x = x) +
  aes(y = y) +
  aes(label = domain) +
  scale_color_manual(values = color_scheme) +
  scale_fill_manual(values = color_scheme) +
  ## --- OPTION 1: PATH ---
  # geom_path(
  #   data = regions,
  #   mapping = aes(x = x, y = y, color = domain_number, group = "1"),
  #   alpha = 1,
  #   size = 0.1
  # ) +
  ## --- OPTION 2: POINT ---
  geom_point(
    data = regions,
    mapping = aes(x = x, y = y, color = domain_number, group = "1"),
    alpha = 0.3,
    size = 1.2,
    shape = 15
  ) +
  guides(color = FALSE) +
  theme(
    legend.position = "none",
    axis.title = element_blank(),
    axis.text = element_blank()
  ) +
  ggrepel::geom_label_repel(
    seed = 123, 
    size = 2, 
    show.legend = F, 
    min.segment.length = 0, 
    color = "black"
  ) +
  coord_fixed() +
  scale_x_continuous(expand = c(0, 0), limits = c(0, NA)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  labs(
    title = paste("Locations of top", top_count, "search results"),
    subtitle = paste("Websites for terms:", plot_terms),
    caption = paste("Mean location and regions of ", upper_limit, "URLs")
  ) +
  my_theme2 +
  theme(
    panel.grid = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) +
  NULL -> locations_small

ggpubr::ggarrange(locations_small) +
  theme(
    plot.background = element_rect(fill = "grey50", color = "grey50"),
    plot.title = element_text(color = "white"),
    plot.subtitle = element_text(color = "white"),
    plot.margin = margin(15, 15, 15, 15),
    plot.caption = element_text(color = "white"),
    panel.background = element_rect(fill = "grey50", color = "grey50"),
    panel.grid = element_line(color = "grey50", size = 1),
    axis.title.x = element_text(color = "white"),
    axis.title.y = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    legend.position = "None"
  )

ggsave(filename = here("output", "locationssmall.pdf"), width = 6, height = 5)
# ggsave(filename = here("output", "locationssmall.png"), width = 6, height = 7)
```


```{r}
# --- plot generics 
n_colors <- dim(regions %>% select(domain_number) %>% unique())[1]
# color_scheme <- viridis::viridis(n_colors) %>% sample()
color_scheme <- grDevices::topo.colors(n_colors) %>% sample()
# color_scheme <- grDevices::terrain.colors(n_colors) %>% sample()
# color_scheme <- grDevices::rainbow(n_colors) %>% sample()
# color_scheme <- colorRamps::blue2red(n_colors) %>% sample()
# color_scheme <- colorRamps::ygobb(n_colors) %>% sample()
# color_scheme <- colorspace::rainbow_hcl(n_colors) %>% sample()
# color_scheme <- colorRamps::matlab.like(n_colors) %>% sample()

# --- format data
all_data %>% 
  filter(country == "DE") %>% 
  filter(search_date == "2017-09-20") %>% 
  mutate(rank = 10 - rank) %>% 
  filter(rank > 0) %>% 
  mutate(rank = factor(rank, levels = c(1:10), labels = paste("Rank", 10:1))) %>% 
  create_coordinates(gghid) -> plot_data

# --- plot
ggplot(plot_data) +
  scale_color_manual(values = color_scheme) +
  geom_point(
    data = regions,
    mapping = aes(x = x, y = y, color = domain_number, group = "1"),
    alpha = 0.1,
    size = 2,
    shape = 15
  ) +
  new_scale_color() +
  geom_point(
    data = plot_data,
    mapping = aes(x = x, y = y, color = keyword, size = as.numeric(rank)),
    color = "white",
    alpha = 0.1
  ) +
  ggrepel::geom_label_repel(
    data = label_positions,
    mapping = aes(x = x, y = y, label = domain),
    seed = 123,
    size = 2,
    show.legend = F,
    min.segment.length = 0,
    segment.size = 0.3,
    fill = "black",
    color = "grey80",
    alpha = 0.5
  ) +
  coord_fixed() +
  facet_wrap(. ~ keyword) +
  my_theme2 +
  theme(
    panel.grid = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) -> singleplot

# --- save
ggsave(here::here("output", "test.pdf"))  
```



```{r}

# --- plot generics 
n_colors <- dim(regions %>% select(domain_number) %>% unique())[1]
# color_scheme <- viridis::viridis(n_colors) %>% sample()
color_scheme <- grDevices::topo.colors(n_colors) %>% sample()
# color_scheme <- grDevices::terrain.colors(n_colors) %>% sample()
# color_scheme <- grDevices::rainbow(n_colors) %>% sample()
# color_scheme <- colorRamps::blue2red(n_colors) %>% sample()
# color_scheme <- colorRamps::ygobb(n_colors) %>% sample()
# color_scheme <- colorspace::rainbow_hcl(n_colors) %>% sample()
# color_scheme <- colorRamps::matlab.like(n_colors) %>% sample()

# --- format data
all_data %>% 
  filter(country == "DE") %>% 
  filter(
    search_date == "2017-09-22" |
    search_date == "2017-09-23" |
    search_date == "2017-09-24"
  ) %>% 
  mutate(rank = 10 - rank) %>% 
  filter(rank > 0) %>% 
  mutate(rank = factor(rank, levels = c(1:10), labels = paste("Rank", 10:1))) %>% 
  create_coordinates(gghid) -> plot_data

# --- plot
ggplot(plot_data) +
  scale_color_manual(values = color_scheme) +
  geom_point(
    data = regions,
    mapping = aes(x = x, y = y, color = domain_number, group = "1"),
    alpha = 0.1,
    size = 2,
    shape = 15
  ) +
  new_scale_color() +
  geom_point(
    data = plot_data,
    mapping = aes(x = x, y = y, color = keyword, size = as.numeric(rank)),
    color = "white",
    alpha = 0.1,
    shape = 16
  ) +
  ggrepel::geom_label_repel(
    data = label_positions,
    mapping = aes(x = x, y = y, label = domain),
    seed = 123,
    size = 2,
    show.legend = F,
    min.segment.length = 0,
    segment.size = 0.3,
    fill = "black",
    color = "grey80",
    alpha = 0.5
  ) +
  coord_fixed() +
  facet_grid(rows = vars(search_date), cols = vars(keyword)) +
  # facet_wrap(. ~ keyword) +
  my_theme2 +
  theme(
    panel.grid = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) -> singleplot

# --- save
ggsave(here::here("output", "multiframe.png"), width = 8, height = 12)  


```


```{r animate_clouds}

# HERE WE ARE ----

all_data %>% 
  filter(country == "DE") %>% 
  filter(keyword == "CDU") %>% 
  mutate(rank = 10 - rank) %>% 
  filter(rank > 0) %>% 
  mutate(rank = factor(rank, levels = c(1:10), labels = paste("Rank", 10:1))) %>% 
  sample_frac(0.01) %>% 
  create_coordinates(gghid) %>% 
  mutate(search_date = ymd(search_date))  -> anim_cloud_data


anim_cloud_data %>% pull(search_date) %>% unique() %>% length() -> frame_pred

ggplot(anim_cloud_data) +
  scale_color_manual(values = color_scheme) +
  guides(color = FALSE) +
  geom_point(
    data = regions,
    mapping = aes(x = x, y = y, color = domain_number, group = "1"),
    alpha = 0.1,
    size = 2,
    shape = 15
  ) +
  new_scale_color() +
  geom_point(
    data = plot_data,
    mapping = aes(x = x, y = y, color = keyword, size = as.numeric(rank)),
    color = "white",
    alpha = 0.1,
    shape = 16
  ) +
  ggrepel::geom_label_repel(
    data = label_positions,
    mapping = aes(x = x, y = y, label = domain),
    seed = 123,
    size = 2,
    show.legend = F,
    min.segment.length = 0,
    segment.size = 0.3,
    fill = "black",
    color = "grey80",
    alpha = 0.5
  ) +
  coord_fixed() +
  #facet_grid(rows = vars(search_date), cols = vars(keyword)) +
  # facet_wrap(. ~ keyword) +
  my_theme2 +
  theme(
    panel.grid = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) +
  theme(legend.position = "none") +
  transition_time(search_date) -> p



{
animate(p, renderer = gifski_renderer(), width = 800, height = 800, res = 70, fps = 1, duration = frame_pred)
beep()
}
anim_save(here("output", "video_preview.gif"))

```




# Single Frame Visualization

```{r single_frame}

repel_label <- ggrepel::geom_label_repel(data = label_positions,
                                         mapping = aes(x = x, y = y, label = domain),
                                         seed = 123, size = 2, show.legend = F, min.segment.length = 0, color = "black")

label_label <- geom_text(data = label_positions,
                                         mapping = aes(x = x, y = y, label = domain), color = "gray")


path_data <- data.frame(gghid = c(1:upper_limit)) %>% create_coordinates(gghid)

all_data %>%
  #filter(keyword %in% c("AfD", "CDU")) %>% 
  mutate(rank = 10 - rank) %>% 
  filter(rank > 1) %>%
  mutate(rank = factor(rank, levels = c(0:10), labels = paste("Rank", 11:1))) %>% 
  filter(search_type == "search") %>%
  filter(country == "DE") %>%
  filter(search_date == "2017-09-20") %>% pull(person_id) %>% n_distinct() 



all_data %>%
  #filter(keyword %in% c("AfD", "CDU")) %>%
  mutate(rank = 10 - rank) %>%
  filter(rank > 0) %>%
  mutate(rank = factor(
    rank,
    levels = c(0:10),
    labels = paste("Rank", 11:1)
  )) %>%
  filter(search_type == "search") %>%
  filter(country == "DE") %>%
  filter(search_date == "2017-09-20") %>%
  create_coordinates(gghid) %>%
  mutate(rank = as.factor(rank)) %>%
  ggplot() +
  scale_color_manual(values = color_scheme) +
  # scale_color_manual(values = c("#0000FF", "#FFFF00"), guide = "none") +
  geom_path(
    data = regions,
    mapping = aes(
      x = x,
      y = y,
      color = domain_number,
      group = "1"
    ),
    inherit.aes = FALSE,
    alpha = 0.3
  ) +
  labs(color = "Region") +
  guides(color = FALSE) +
  new_scale_color() +
  scale_color_manual(values = selected_colors) +
  aes(
    x = x,
    y = y,
    color = keyword,
    label = domain
  ) + #, size = rank) +
  repel_label +
  #label_label+
  geom_point(aes(size = rank), alpha = 0.01) +
  labs(
    title = "Hilbert Plot for top search results for AfD and CDU",
    size = "Rank",
    color = "Search Term",
    subtitle = "Differences for the AfD and CDU, Date: 2017-09-20",
    caption = paste(
      "Results for 1298 unique users. Individual results use 0.01 alpha blending."
    )
  ) +
  #coord_fixed() +
  #facet_wrap(~keyword, nrow = 1) +
  guides(colour = guide_legend(override.aes = list(alpha = 1, size = 5))) +
  guides(size = guide_legend(override.aes = list(alpha = 0.5))) +
  my_theme -> singleplot

singleplot

ggsave(plot = singleplot, filename = here("output", "singleframe.pdf"), width = 8, height = 5)
```




# Two Frames

```{r create_two_figures}
all_data %>%
  #filter(keyword %in% c("AfD", "CDU")) %>%
  mutate(rank = 10 - rank) %>%
  filter(rank > 0) %>%
  mutate(rank = factor(
    rank,
    levels = c(0:10),
    labels = paste("Rank", 11:1)
  )) %>%
  filter(search_type == "search") %>%
  filter(country == "DE") %>%
  filter(search_date == "2017-09-20") %>%
  create_coordinates(gghid) %>%
  mutate(rank = as.factor(rank)) %>%
  ggplot() +
  scale_color_manual(values = color_scheme) +
  # scale_color_manual(values = rep(RColorBrewer::brewer.pal(1, "Set1")[-3],2)) +
  #scale_color_manual(values = c("#0000FF", "#FFFF00", ), guide = "none") +
  geom_path(
    data = regions,
    mapping = aes(
      x = x,
      y = y,
      color = domain_number,
      group = "1"
    ),
    inherit.aes = FALSE,
    alpha = 0.8,
    size = 0.1
  ) +
  labs(color = "Region") +
  guides(color = FALSE) +
  new_scale_color() +
  scale_color_manual(values = selected_colors) +
  aes(
    x = x,
    y = y,
    color = keyword,
    label = domain
  ) + #, size = rank) +
  repel_label +
  #label_label+
  geom_point(aes(size = rank), alpha = 0.01) +
  guides(colour = guide_legend(override.aes = list(alpha = 1, size = 5))) +
  guides(size = guide_legend(override.aes = list(alpha = 0.5))) +
  guides(size = FALSE) +
  guides(colour = FALSE) +
  labs(subtitle = "Date: 2017-09-20") +
  facet_wrap(~keyword, nrow = 1) +
  coord_fixed() +
  my_theme -> singleplot1


ggsave("output/test2.pdf")
singleplot1 
```


```{r create_two_figures2}
all_data %>%
  #filter(keyword %in% c("AfD", "CDU")) %>%
  mutate(rank = 10 - rank) %>%
  filter(rank > 0) %>%
  mutate(rank = factor(
    rank,
    levels = c(0:10),
    labels = paste("Rank", 11:1)
  )) %>%
  filter(search_type == "search") %>%
  filter(country == "DE") %>%
  filter(search_date == "2017-09-16") %>%
  create_coordinates(gghid) %>%
  mutate(rank = as.factor(rank)) %>%
  ggplot() +
  scale_color_manual(values = c("#0000FF", "#FFFF00"), guide = "none") +
  geom_path(
    data = regions,
    mapping = aes(
      x = x,
      y = y,
      color = domain_number,
      group = "1"
    ),
    inherit.aes = FALSE,
    alpha = 0.3
  ) +
  labs(color = "Region") +
  guides(color = FALSE) +
  new_scale_color() +
  scale_color_manual(values = selected_colors) +
  aes(
    x = x,
    y = y,
    color = keyword,
    label = domain
  ) + #, size = rank) +
  repel_label +
  #label_label+
  geom_point(aes(size = rank), alpha = 0.01) +
  guides(colour = guide_legend(override.aes = list(alpha = 1, size = 5))) +
  guides(size = guide_legend(override.aes = list(alpha = 0.5))) +
  guides(size = FALSE) +
  guides(colour = FALSE) +
  labs(subtitle = "Date: 2017-09-20") +
  facet_wrap(~keyword, nrow = 1) +
  coord_fixed() +
  my_theme -> singleplot3


all_data %>%
  #filter(keyword %in% c("AfD", "CDU")) %>%
  mutate(rank = 10 - rank) %>%
  filter(rank > 0) %>%
  mutate(rank = factor(
    rank,
    levels = c(0:10),
    labels = paste("Rank", 11:1)
  )) %>%
  filter(search_type == "search") %>%
  filter(country == "DE") %>%
  filter(search_date == "2017-09-24") %>%
  create_coordinates(gghid) %>%
  mutate(rank = as.factor(rank)) %>%
  ggplot() +
  scale_color_manual(values = c("#0000FF", "#FFFF00"), guide = "none") +
  geom_path(
    data = regions,
    mapping = aes(
      x = x,
      y = y,
      color = domain_number,
      group = "1"
    ),
    inherit.aes = FALSE,
    alpha = 0.3
  ) +
  labs(color = "Region") +
  guides(color = FALSE) +
  new_scale_color() +
  scale_color_manual(values = selected_colors) +
  aes(
    x = x,
    y = y,
    color = keyword,
    label = domain
  ) + #, size = rank) +
  repel_label +
  #label_label+
  geom_point(aes(size = rank), alpha = 0.01) +
  guides(colour = guide_legend(override.aes = list(alpha = 1, size = 5))) +
  guides(size = guide_legend(override.aes = list(alpha = 0.5))) +
  guides(size = FALSE) +
  guides(colour = FALSE) +
  labs(subtitle = "Date: 2017-09-24") +
  facet_wrap(~keyword, nrow = 1) +
  coord_fixed() +
  my_theme -> singleplot2

fullplot <-
  singleplot1 / singleplot3 / singleplot2 + plot_annotation(
    title = "Hilbert Plot for top search results for AfD and CDU",
    caption = paste(
      "Results for 1298 unique users. Individual results use 0.01 alpha blending."
    )
  )


fullplot 

ggsave(plot = fullplot, filename = here("output", "sidebyside.pdf"), width = 8, height = 12)
```


# Animation

```{r generate_animation_data}

# Start the animation at?
start_date <- "2017-09-20"

anim_data <- all_data %>%
  mutate(rank = 10 - rank) %>% 
  filter(rank > 0) %>%
  mutate(rank = factor(rank, levels = c(0:10), labels = paste("Rank", 11:1))) %>% 
  filter(search_type == "search") %>%
  filter(country == "DE") %>%
  filter(search_date > start_date) %>%  
  create_coordinates(gghid) %>%
  mutate(rank = as.factor(rank))  

anim_data %>% pull(search_date) %>% unique() %>% length() -> frame_pred # how many dates are there?
```


```{r generate_animation}
# create label repel instructions used in the animation
repel_label <- ggrepel::geom_label_repel(
  data = label_positions,
  mapping = aes(x = x, y = y, label = domain),
  seed = 123,
  size = 3,
  show.legend = F,
  min.segment.length = 0,
  color = "black"
)

# creates the animation (without rendering)
anim_data %>%
  ggplot() +
  scale_color_manual(values = c("#0000FF", "#FFFF00"), guide = "none") +
  geom_path(
    data = regions,
    mapping = aes(
      x = x,
      y = y,
      color = domain_number,
      group = "1"
    ),
    inherit.aes = FALSE,
    alpha = 0.3
  ) +
  new_scale_color() +
  aes(
    x = x,
    y = y,
    color = keyword,
    label = domain,
    size = rank
  ) +
  scale_color_manual(values = selected_colors) +
  repel_label +
  #label_label+
  geom_point(alpha = 0.01) +
  labs(
    title = "Hilbert Plot for search results",
    size = "Rank",
    color = "Search Term",
    subtitle = "Date: {frame_time}"
  ) +
  coord_fixed() +
  #facet_wrap(~keyword) +
  guides(colour = guide_legend(override.aes = list(alpha = 1, size = 5))) +
  guides(size = guide_legend(override.aes = list(alpha = 0.5))) +
  my_theme +
  transition_time(search_date) +
  enter_appear() +
  exit_disappear() -> p

```

```{r render_preview}
# low res version
animate(p, renderer = gifski_renderer(), width = 1600, height = 1000, res = 150, fps = 1, duration = frame_pred)
anim_save(here("output", "video_preview.gif"))
```


```{r create_mpg}
# Requirs "ffmpeg" to be installed on the system

if (ffmpeg) {
  animate(p, renderer = ffmpeg_renderer(), width = 1920, height = 1080, fps = 1, duration = frame_pred, res = 200)
  anim_save(here("output", "video_preview.mp4"))
  beep()
}
```


```{r render_full, eval=FALSE, include=FALSE}
# render animation
{
  animate(p, renderer = gifski_renderer(), width = 1200, height = 1200, res = 150, fps = 20, duration = 40)
  anim_save(here("output", "video.gif"))
  beep()
}
```


```{r end, include=FALSE}
all_data %>% select(domain, url) %>% head(50) %>% View()
beep(4)
```




```{r comparison}
temp_data <- all_data %>% 
  filter(search_date == dmy("20-09-2017"))

library(Rtsne) # Load package

dta <- temp_data %>% select(keyword, url, rank, person_id) %>% 
  count(keyword, rank, url)
  
set.seed(42) # Sets seed for reproducibility

our_coal <- function(x){
  coalesce(x, 0L)
}

prepped <- dta %>% 
  pivot_wider(names_from = "url", values_from = "n" ) %>% 
  mutate(keyword = factor(keyword))

prep2 <- prepped %>% mutate_at(vars(3:last_col()), our_coal) %>% 
  mutate(keyword = as.numeric(keyword))



tsne_out <- Rtsne(as.matrix(prep2 %>% select(-keyword, -rank))) # Run TSNE

tsne_out$Y %>% 
  as_tibble() %>% 
  add_column(party = prep2$keyword, rank = prep2$rank) %>% 
  ggplot() +
  aes(x = V1, y = V2, color = factor(party, labels = c("CDU", "AfD")), size = rank) +
  geom_point(alpha = 0.7)



tsne_out

```



